---
title: "Algorithm Aversion"
author: "Kopkow, Angermaier, Rohrer, Sonnleitner"
date: "February 2022"
output:
  pdf_document:
    toc: true
    toc_depth: 2
  html_document:
    toc: true
    toc_depth: 2
---





# Motivation: Erwin


# Data retrieval


# Data processing: Mathias

```{r Libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(tidyverse)
library(tidytext)
library(textdata)
library(dplyr)
library(vader)
library(academictwitteR)
library(data.table)
library(readr)
library(boot)
library(knitr)
```

used libraries

```{r read and group data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 alg.data <- read_csv('algtweetsalgData.csv'
                      )

#write.csv(alg.data,"C:/Users/usr/Documents/algtweetsalgData.csv", row.names = TRUE)


alg.data <- alg.data[, c  ("index" ,"text", "id" ,"created_at", "VADER",
                           "VADERclass", "Business" ,  "Social.Media", 
                           "Technology" ,  "Immutability" ,"Influence", 
                           "Application",   "Aversion",
                           "Year","topic" ) ]

alg.data <- select(alg.data, -'topic')

```


```{r sorting, include=FALSE}
#alg.data %>% group_by(alg.data$topic, alg.data$Year, alg.data$VADERclass) %>% summarise(Sent = #n())-> summ.data
alg.data %>% group_by(alg.data$Year, alg.data$VADERclass) %>% summarise(Sent = n()) -> summ.year
#alg.data %>% group_by(alg.data$topic, alg.data$VADERclass) %>% summarise(Sent = n()) -> summ.topic


#alg.data %>% group_by(topic, Year, VADERclass) %>% summarise(Sent = n()) -> summ.data
alg.data %>% group_by(Year, VADERclass) %>% summarise(Sent = n()) -> summ.year

#adds percentage to yearwise DF
summ.year<- 
  summ.year %>% 
  group_by(Year) %>% 
  mutate(All = sum(Sent),percent=(100*Sent/All))


```

```{r cummulated, include=FALSE}
listofdfs <- list()

#data group for cummulated dataframe

for (i in c(7:13)){
  alg.data %>% 
    filter(alg.data[,i]>=1)%>% 
    mutate(Topic = colnames(alg.data)[i], VADERclass=as.factor(VADERclass))%>% 
    group_by(Year,Topic,VADERclass, .drop=FALSE)%>% 
    summarise(Sent = n(), .groups = "drop") ->listofdfs[[i]]
}
summ.cumm <- bind_rows(listofdfs)


#adds percentage to cummulated DF
summ.cumm <- 
  summ.cumm %>% 
  group_by(Topic, Year) %>% 
  mutate(All = sum(Sent),percent=(100*Sent/All))

summ.cumm
```

```{r topic, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#data group for topic oriented dataframe

listofdfs <- list()

for (i in c(7:13)){
  alg.data %>% 
    filter(alg.data[,i]>=1)%>% 
    mutate(Topic = colnames(alg.data)[i])%>% 
    group_by( VADERclass, Topic) %>% 
    summarise(Sent = n()) ->listofdfs[[i]]
}
summ.topic <- bind_rows(listofdfs)

#adds percentage to topicwise DF
summ.topic<- 
  summ.topic %>% 
  group_by(Topic) %>% 
  mutate(All = sum(Sent),percent=(100*Sent/All))



```



```{r wordgrouptest}
#--------------Test wordgroups---------------------
listofdfs <- list()


for (i in c(7:13)){
  alg.data %>% 
    filter(alg.data[,i]>=1)%>% 
    mutate(Topic = colnames(alg.data)[i])%>% 
    sample_n(size = 20)%>% 
  group_by( VADERclass, Topic)  ->listofdfs[[i]]
}
Wordgrouptest<- bind_rows(listofdfs)
```



# Analysis 

The following chapter covers the results of the sentiment analysis of tweets over the years 2010 to 2021 , for which we used the Vader tool.  Values between -0.3 and 0.3 were classified as neutral. Those between 0.3 and 1 were classified as positive, as negative between -0.3 and -0.7 and finally as aversive values between -0.7 and -1.   

A Confidence interval based on 10000 bootstrap replications was calculated. It revealed that with a probability of 95% that the mean value of the sentiment analysis falls between 0.0766 and 0.1349.


```{r bootstrap, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#--------------Bootstraping---------------------
listofdfs <- list()

## Sample of 100 tweets per topic
for (i in c(7:13)){
  alg.data %>% 
    filter(alg.data[,i]>=1)%>% 
    mutate(Topic = colnames(alg.data)[i])%>% 
    mutate(Neutral = VADERclass=="Neutral")%>% 
    mutate(Positive = VADERclass=="Positive")%>% 
    mutate(Negative = VADERclass=="Negative")%>% 
    mutate(Aversive = VADERclass=="Aversive")%>% 
    sample_n(size = 100)%>% 
    group_by( VADERclass, Topic) ->listofdfs[[i]]
}
bootstrap<- bind_rows(listofdfs)
bootstrap %>% select(Year,Topic,VADER,VADERclass,Neutral,Positive,Negative,Aversive) -> bootstrap
bootstrap 



bootstrap  -> ObservedHeight
ObservedHeights <- ObservedHeight$VADER
  
mean(ObservedHeights)
ReturnMean <- function(datav, sampleindices) 
  
{
  d <- datav[sampleindices] # we will use this for bootstrapping
  return( mean(d) )
}

## Bootstrapping with 10000 replications
results <- boot(data=as.vector(ObservedHeights), statistic=ReturnMean, R=10000)


hist(results$t)
results



```


```{r plot topic year, eval=FALSE, include=FALSE}
#-----------------Topic-----------------------
topics = c('Business','Social.Media','Technology','Influence','Application','Aversion')


for (i in 1:length(topics)){
  
  summ.cumm %>% 
    filter(Topic==topics[i]) %>%
    with(plot(Year, Sent, main =topics[i],xlab = 'Analyzed Year', ylab = 'Tweets'))
  summ.cumm %>% 
    filter(Topic==topics[i]) %>% 
    with(lines(unique(Year), Sent[VADERclass=='Positive'], col = 3) )
  summ.cumm %>% 
    filter(Topic==topics[i]) %>%
    with(lines(unique(Year), Sent[VADERclass=='Neutral'], col = 1))
  summ.cumm %>% 
    filter(Topic==topics[i]) %>%
    with(lines(unique(Year), Sent[VADERclass=='Negative'], col = 2))
  summ.cumm %>% 
    filter(Topic==topics[i]) %>%
    with(lines(unique(Year), Sent[VADERclass=='Aversive'], col = 4))
  summ.cumm %>% 
    filter(Topic==topics[i]) %>%
    with(legend("topright", legend=c("neutral", "positive", "negative", "aversive"), col=c("black","green", "red"), lty=1:1, cex=0.8)) 
}
```


## Progression over the years

The diagram shows the percentage progression of the results of the sentiment analysis of tweets over the years 2010 to 2021.A total of 143271 tweets were analyzed. Since all tweets that could not be evaluated in the sentiment analysis were classified as neutral, the highest number of tweets was yielded in the neutral category while the fewest tweets were classified as aversive.

```{r yearplot, echo=FALSE, warning=FALSE}
plot(summ.year$Year, summ.year$percent, main ="Progression over the years",xlab = 'Analyzed year', ylab = 'Percent',cex.lab=1, cex.axis=1, cex.main=2, cex.sub=1)
lines(unique(summ.year$Year), summ.year$percent[summ.year$VADERclass=='Positive'], col = "green", lwd=2)
lines(unique(summ.year$Year), summ.year$percent[summ.year$VADERclass=='Neutral'], col = "black", lwd=2)
lines(unique(summ.year$Year), summ.year$percent[summ.year$VADERclass=='Negative'], col = "blue", lwd=2)
lines(unique(summ.year$Year), summ.year$percent[summ.year$VADERclass=='Aversive'], col = "red",lwd=2)
legend("topright", legend=c("positive", "neutral", "negative", "aversive"), col=c("green","black", "blue", "red"), lty=1:1,lwd=2, cex=.7)
```

Over time, the number of neutral tweets decreases. In 2010, there were 6934 neutral tweets which amounts to 58.3% of the yearly total. In 2015, the highest number of neutral tweets were posted, with an absolute of 7641 tweets posted (63.8% of the yearly total). In 2019, the lowest number of neutral tweets (5241, 43.7%) was posted. 2021 yielded similar numbers (5254, 43.8%). Over the last 3 years, the number of neutral tweets remained at the same level. 

An increasing trend can be seen in the number of positive tweets. In 2010, there were 3827 positive tweets, representing 32.2% of the yearly total. In 2011, the least amount of tweets 3171 (26.7%) were posted. In 2019, the most positive tweets were posted with absolute 4878 (40.7%) posted. Last year, 2021, a total of 4868 positive tweets were posted, which is 40.6% of the annual total. The number of positive tweets remained high over he last 3 years, with a dip in 2020 (3908 total, 32.6%).

Negative tweets show an increasing trend. In 2010, there were 1008 negative tweets constituting 8.5% of the annual total. In 2020 the highest number of negative tweets were posted with absolute 1867 tweets (15.6%) posted. In 2015, the least amount of negative tweets was posted (918, 7.7%). In the last year analyzed, 2021, the number of negative tweets remained high with 1429 total, 11.9% of the annual. 

The number of aversive tweets behaves similarly to that of negative tweets. 2011 113 0.95% there were the fewest were 2014 105 and 0.88% with the most there were 2020 968 8.1% and 2021 there were 3.7% and 449 tweets.

## Distribution of classes by topic

This graph shows the different topics Business, Social Media, Technology, Immutability, Influence, Application and Aversion as well as the percentage distribution of the VADER classes Aversive, Negative, Neutral, and Positive.


```{r topicplot,echo=FALSE}

ggplot(data=summ.topic, 
       aes(x=Topic, y=percent, fill=VADERclass)) + 
  ggtitle("Topics 2010-2021") +
  geom_bar(stat="identity", position=position_dodge(), colour="black")+
  theme(axis.text=element_text(size=8),plot.title = element_text(color="Black", size=6, face="bold", hjust = 0.5),
        legend.text=element_text(size=6),
  axis.title=element_text(size=8,face="bold"))

```
```{r conf, include=FALSE}
# Bootstrap 95% CI for R-Squared
boot.ci(results, type="bca")
```

The topic Aversion has the most aversive tweets with 16.8% and 35% negative tweets, so there are more negative tweets in this topic than positive 20%. The smallest amount occurs in Application; here, there are no aversive tweets at all. In the topic Social media, 28.9% of the tweets are positive, 13.6% negative and 3.7% aversive. In total, this was also the topic in which the most tweets occurred with a total of 42020.


# Conclusion: 


# Critique: Alina


# Github Repository

https://github.com/sonnleit/AlgorithmAversion

